---
title: "Single Order restoration plots"
output: html_document
date: "2023-06-23"
---
##Creating a 4x4 matrix plot wrt watershed load (percent nitrate removed from the watershed) or local load (percent nitrate removed from a river order with respect to the load entering the respective order). Plot by river outlet.

#Housekeeping
```{r}
library(patchwork)

test <- inun_1stO %>%
  filter(river == "2-2" & ti_tot_min > 0 & plan == "1st-20p" )
```

#Loads to the Watershed
```{r}
OrderLoads_kg <- data.frame(Order = c("1st", "1st","1st", "1st", 
                                      "2nd", "2nd", "2nd", "2nd", 
                                      "3rd", "3rd", "3rd", "3rd", 
                                      "4th", "4th", "4th", "4th"),
                            Load = c(141.9, 103, 91.5, 65.9,
                                     120.6,126.2,74.5,3,
                                     680.4,545.8,325.8,26.9,
                                     3620.2,2878.4,1770.8,149.5),
                            storm = c("Q2", "Q1", "Q0.5", "Qmonth", 
                                      "Q2", "Q1", "Q0.5", "Qmonth", 
                                      "Q2", "Q1", "Q0.5", "Qmonth", 
                                      "Q2", "Q1", "Q0.5", "Qmonth"))

OrderLoads_kg$storm <- factor(OrderLoads_kg$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qmonth"))
OrderLoads_kg%>%ggplot()+
  geom_line(aes(Order, Load,color = storm, group = storm))+
  geom_point(aes(Order, Load,color = storm))+
  ylim(0,4000)+
  xlab("River Order")+
  ylab(expression(NO[3]~Load~(kg)))+
  ggtitle(expression(atop("NO"[3]*" Load by Individual Stream")))+ 
  theme(text = element_text(size = 8), 
        title = element_text(size = 10))   
ggsave("Figures/OrderLoadsKg.png", dpi=500, height=4, width=5, units="in")

# OrderLoads_kg$storm <- factor(OrderLoads_kg$storm,                 # Re-level group factor
#                          levels = c("Qmonth", "Q0.5", "Q1", "Q2"))
# OrderLoads_kg %>%
#   group_by(storm)%>%
#   summarise(totLoad = sum(Load))%>%
#   ggplot()+
#   geom_line(aes(storm, totLoad, group = 1))+
#   geom_point(aes(storm, totLoad))+
#   ylim(0,5000)+
#   xlab("Storm Size")+
#   ylab(expression(Total~NO[3]~Load~(kg)))+
#   ggtitle(expression(atop("4"^th*"-order Watershed NO"[3]*"Load by Storm Size")))
# ggsave("Exports/WatershedLoadsKg.png", dpi=500, height=4, width=4, units="in")
```

```{r}
shedLoads_kg <- data.frame(Order = c("1st", "1st","1st", "1st", 
                                      "2nd", "2nd", "2nd", "2nd", 
                                      "3rd", "3rd", "3rd", "3rd", 
                                      "4th", "4th", "4th", "4th"),
                            Load = c(5.9, 4.3, 3.8, 2.7,
                                     43.7,38.2,27.7,11.5,
                                     471,387,246,48,
                                     4563,3653,2263,245),
                            storm = c("Q2", "Q1", "Q0.5", "Qm", 
                                      "Q2", "Q1", "Q0.5", "Qm", 
                                      "Q2", "Q1", "Q0.5", "Qm", 
                                      "Q2", "Q1", "Q0.5", "Qm"))

shedLoads_kg$storm <- factor(shedLoads_kg$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
shedLoads_kg%>%ggplot()+
  geom_line(aes(Order, Load,color = storm, group = storm))+
  geom_point(aes(Order, Load,color = storm))+
  ylim(0,5000)+
  xlab("Watershed Order")+
  ylab(expression(atop("NO"[3]*" Load to the Watershed (kg)")))+
  ggtitle(expression(Watershed~NO[3]~Loads))+
  theme(text = element_text(size = 8), 
        title = element_text(size = 10))   
ggsave("Figures/shedOrderLoadsKg.png", dpi=500, height=4, width=5, units="in")


```

#Calcs for cumulative removal
```{r}
# Reordering storms so plots have them in order
NO3_1stO$storm <- factor(NO3_1stO$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
NO3_2ndO$storm <- factor(NO3_2ndO$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
NO3_3rdO$storm <- factor(NO3_3rdO$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
NO3_4thO$storm <- factor(NO3_4thO$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))

NO3_1stO <-   NO3_1stO %>% 
    transform(k10_PerCumRem = ave(k10_percentWLR, storm, plan, FUN = cumsum),
              km_PerCumRem = ave(km_percentWLR, storm, plan, FUN = cumsum),
              k90_PerCumRem = ave(k90_percentWLR, storm, plan, FUN = cumsum)) %>%
    transform(k90_.5PerCumRem = ave(k90_pWLR_.5mgL, storm, plan, FUN = cumsum),
              k90_2PerCumRem = ave(k90_pWLR_2mgL, storm, plan, FUN = cumsum))

NO3_2ndO <-   NO3_2ndO %>% 
    transform(k10_PerCumRem = ave(k10_percentWLR, storm, plan, FUN = cumsum),
              km_PerCumRem = ave(km_percentWLR, storm, plan, FUN = cumsum),
              k90_PerCumRem = ave(k90_percentWLR, storm, plan, FUN = cumsum))%>%
    transform(k90_.5PerCumRem = ave(k90_pWLR_.5mgL, storm, plan, FUN = cumsum),
              k90_2PerCumRem = ave(k90_pWLR_2mgL, storm, plan, FUN = cumsum))

NO3_3rdO <-   NO3_3rdO %>% 
    transform(k10_PerCumRem = ave(k10_percentWLR, storm, plan, FUN = cumsum),
              km_PerCumRem = ave(km_percentWLR, storm, plan, FUN = cumsum),
              k90_PerCumRem = ave(k90_percentWLR, storm, plan, FUN = cumsum))%>%
    transform(k90_.5PerCumRem = ave(k90_pWLR_.5mgL, storm, plan, FUN = cumsum),
              k90_2PerCumRem = ave(k90_pWLR_2mgL, storm, plan, FUN = cumsum))

NO3_4thO <-   NO3_4thO %>% 
    transform(k10_PerCumRem = ave(k10_percentWLR, storm, plan, FUN = cumsum),
              km_PerCumRem = ave(km_percentWLR, storm, plan, FUN = cumsum),
              k90_PerCumRem = ave(k90_percentWLR, storm, plan, FUN = cumsum))%>%
    transform(k90_.5PerCumRem = ave(k90_pWLR_.5mgL, storm, plan, FUN = cumsum),
              k90_2PerCumRem = ave(k90_pWLR_2mgL, storm, plan, FUN = cumsum))

group_keys(NO3_1stO)

save(NO3_1stO, NO3_2ndO, NO3_3rdO, NO3_4thO,
    file = "C:/Users/morganao/Documents/CBT_Oehler2023/9_Saved_Dataframes/SO_cumu_plot_df.RData")
```

#4th order-watershed removal- cumulative
```{r plot-wider, fig.width=10, fig.height=10}
#1
one <- NO3_1stO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(expression(atop("%NO"[3]*"Removed", "U.S. of 1"^st*"-order outlets")))+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#5
five <- NO3_1stO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(expression(atop("%NO"[3]*"Removed", "U.S. of 2"^nd*"-order outlets")))+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#9
nine <- NO3_1stO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(expression(atop("%NO"[3]*"Removed", "U.S. of 3"^rd*"-order outlets")))+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#13
thirteen <- NO3_1stO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(expression(atop("Percent of 1"^st*"-Order", " Rivers Restored")))+
  ylab(expression(atop("%NO"[3]*"Removed", "U.S. of 4"^th*"-order outlet")))+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)

#2
two <- NO3_2ndO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "Total Length of 2nd-order Rivers Restored [km]", breaks = seq(0,35,5)))+
  ylim(0,1)
#6
six <- NO3_2ndO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#10
ten <- NO3_2ndO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#14
fourteen <- NO3_2ndO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(expression(atop("Percent of 2"^nd*"-Order", " Rivers Restored")))+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)

#3
three <- NO3_3rdO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#7
seven <- NO3_3rdO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#11
eleven <- NO3_3rdO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
 ylim(0,1)
#15
fifteen <- NO3_3rdO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(expression(atop("Percent of 3"^rd*"-Order", " Rivers Restored")))+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#4
four <- NO3_4thO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#8
eight <- NO3_4thO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  ylim(0,1)+
  scale_x_continuous(breaks=seq(0,100,by=20))
#12
twelve <- NO3_4thO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)
#16
sixteen <- NO3_4thO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_PerCumRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_PerCumRem, color = storm), size = 0.5)+
  xlab(expression(atop("Percent of 4"^th*"-Order", "River Restored")))+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,1)


one+
  scale_x_continuous(sec.axis = sec_axis(~. * 0.43891, 
                     name = expression(atop("Total Length of 1"^st*"-order","Rivers Restored [km]")), 
                     breaks = seq(0,50,10)))+
two+
  scale_x_continuous(sec.axis = sec_axis(~. * 0.30175,
                     name = expression(atop("Total Length of 2"^nd*"-order"," Rivers Restored [km]")),
                     breaks = seq(0,35,5)))+
three+
  scale_x_continuous(sec.axis = sec_axis(~. * 0.25603, 
                     name = expression(atop("Total Length of 3"^rd*"-order"," Rivers Restored [km]")), 
                     breaks = seq(0,30,5)))+
four+
  scale_x_continuous(sec.axis = sec_axis(~. * 0.30785, 
                     name = expression(atop("Total Length of 4"^th*"-order"," Rivers Restored [km]")), 
                     breaks = seq(0,35,5)))+
five+six+seven+eight+nine+ten+eleven+twelve+thirteen+fourteen+fifteen+sixteen+
  plot_layout(ncol = 4, guides = "collect")+
  plot_annotation(title = expression("Percent NO"[3]*" Removed from the Watershed Cumulatively (k"[m]*")"), 
                  caption = "U.S.- Upstream",
                  theme = theme(title = element_text(size = 12, face = 2)))&
  theme(text = element_text(size = 10))
  ggsave("Figures/SOmatrixWSL_km_uni.png", dpi=500,  units="in")
```

```{r}
ggsave("Exports/SOmatrixWSL_km_uni.png", dpi=500,  units="in")
#ggsave("Exports/SOmatrixWSL_km_non.png", dpi=500, height=4, width=5, units="in")
```

#k10 cumulative
```{r}
#1
one <- NO3_1stO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed \n U.S. of 1st order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "Total Length of 1st-order Rivers Restored [km]", breaks = seq(0,50,10)))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)
#5
five <- NO3_1stO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed \n U.S. of 2nd order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)
#9
nine <- NO3_1stO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed\n U.S. of 3rd order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)
#13
thirteen <- NO3_1stO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab("% of 1st-order\n Streams Restored")+
  ylab("%NO3 Removed \n U.S. of 4th order outlet")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)

#2
two <- NO3_2ndO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "Total Length of 2nd-order Rivers Restored [km]", breaks = seq(0,35,5)))+
 ylim(0,0.1)+
        theme(aspect.ratio = 1)
#6
six <- NO3_2ndO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)
#10
ten <- NO3_2ndO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)
#14
fourteen <- NO3_2ndO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab("% of 2nd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
 ylim(0,0.1)+
        theme(aspect.ratio = 1)

#3
three <- NO3_3rdO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "Total Length of 3rd-order Rivers Restored [km]", breaks = seq(0,30,5)))+
 ylim(0,0.1)+
        theme(aspect.ratio = 1)
#7
seven <- NO3_3rdO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)
#11
eleven <- NO3_3rdO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
ylim(0,0.1)+
        theme(aspect.ratio = 1)
#15
fifteen <- NO3_3rdO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab("% of 3rd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
 ylim(0,0.1)+
        theme(aspect.ratio = 1)

#4
four <- NO3_4thO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "Total Length of 4th-order River Restored [km]", breaks = seq(0,35,5)))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)
#8
eight <- NO3_4thO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
 ylim(0,0.1)+
  scale_x_continuous(breaks=seq(0,100,by=20))+
        theme(aspect.ratio = 1)
#12
twelve <- NO3_4thO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)
#16
sixteen <- NO3_4thO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k10_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k10_PerCumRem, color = storm), size = 0.2)+
  xlab("% of 4th-order \n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,0.1)+
        theme(aspect.ratio = 1)


one+theme(text = element_text(size = 5))+
two+theme(text = element_text(size = 5))+
three+theme(text = element_text(size = 5))+
four+theme(text = element_text(size = 5))+
five+theme(text = element_text(size = 5))+
six+theme(text = element_text(size = 5))+
seven+theme(text = element_text(size = 5))+
eight+theme(text = element_text(size = 5))+
nine+theme(text = element_text(size = 5))+
ten+theme(text = element_text(size = 5))+
eleven +theme(text = element_text(size = 5))+ 
twelve +theme(text = element_text(size = 5))+ 
thirteen+theme(text = element_text(size = 5))+
fourteen+theme(text = element_text(size = 5))+
fifteen+theme(text = element_text(size = 5))+
sixteen+theme(text = element_text(size = 5))+
            plot_layout(ncol = 4, guides = "collect")+
            plot_annotation(title = 'Percent NO3 Removed from the Watershed Cumulatively (k10)', 
                            theme = theme(title = element_text(size = 8, face = 2)))
ggsave("Exports/SOmatrixWSL_uni_k10.png", dpi=500, height=4, width=5, units="in")
#ggsave("Exports/SOmatrixWSL_non_k10.png", dpi=500, height=4, width=5, units="in")
```


#k90 cumulative
```{r}
#1
one <- NO3_1stO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed \n U.S. of 1st order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "Total Length of 1st-order Rivers Restored [km]", breaks = seq(0,50,10)))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#5
five <- NO3_1stO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed \n U.S. of 2nd order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#9
nine <- NO3_1stO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed\n U.S. of 3rd order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#13
thirteen <- NO3_1stO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab("% of 1st-order\n Streams Restored")+
  ylab("%NO3 Removed \n U.S. of 4th order outlet")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)

#2
two <- NO3_2ndO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "Total Length of 2nd-order Rivers Restored [km]", breaks = seq(0,35,5)))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#6
six <- NO3_2ndO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#10
ten <- NO3_2ndO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#14
fourteen <- NO3_2ndO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab("% of 2nd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)

#3
three <- NO3_3rdO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "Total Length of 3rd-order Rivers Restored [km]", breaks = seq(0,30,5)))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#7
seven <- NO3_3rdO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#11
eleven <- NO3_3rdO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#15
fifteen <- NO3_3rdO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab("% of 3rd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)

#4
four <- NO3_4thO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "Total Length of 4th-order River Restored [km]", breaks = seq(0,35,5)))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#8
eight <- NO3_4thO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  ylim(0,20)+
  scale_x_continuous(breaks=seq(0,100,by=20))+
        theme(aspect.ratio = 1)
#12
twelve <- NO3_4thO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)
#16
sixteen <- NO3_4thO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_PerCumRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_PerCumRem, color = storm), size = 0.2)+
  xlab("% of 4th-order \n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,20)+
        theme(aspect.ratio = 1)


one+theme(text = element_text(size = 5))+
two+theme(text = element_text(size = 5))+
three+theme(text = element_text(size = 5))+
four+theme(text = element_text(size = 5))+
five+theme(text = element_text(size = 5))+
six+theme(text = element_text(size = 5))+
seven+theme(text = element_text(size = 5))+
eight+theme(text = element_text(size = 5))+
nine+theme(text = element_text(size = 5))+
ten+theme(text = element_text(size = 5))+
eleven +theme(text = element_text(size = 5))+ 
twelve +theme(text = element_text(size = 5))+ 
thirteen+theme(text = element_text(size = 5))+
fourteen+theme(text = element_text(size = 5))+
fifteen+theme(text = element_text(size = 5))+
sixteen+theme(text = element_text(size = 5))+
            plot_layout(ncol = 4, guides = "collect")+
            plot_annotation(title = 'Percent NO3 Removed from the Watershed Cumulatively (k90)', 
                            theme = theme(title = element_text(size = 8, face = 2)))
ggsave("Exports/SOmatrixWSL_uni_k90.png", dpi=500, height=4, width=5, units="in")
#ggsave("Exports/SOmatrixWSL_non_k90.png", dpi=500, height=4, width=5, units="in")
```
#k90 cumulative 2mgL
```{r}
#1
one <- NO3_1stO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed \n U.S. of 1st order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "Total Length of 1st-order Rivers Restored [km]", breaks = seq(0,50,10)))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#5
five <- NO3_1stO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed \n U.S. of 2nd order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#9
nine <- NO3_1stO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed\n U.S. of 3rd order outlets")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#13
thirteen <- NO3_1stO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab("% of 1st-order\n Streams Restored")+
  ylab("%NO3 Removed \n U.S. of 4th order outlet")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)

#2
two <- NO3_2ndO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "Total Length of 2nd-order Rivers Restored [km]", breaks = seq(0,35,5)))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#6
six <- NO3_2ndO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#10
ten <- NO3_2ndO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#14
fourteen <- NO3_2ndO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab("% of 2nd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)

#3
three <- NO3_3rdO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "Total Length of 3rd-order Rivers Restored [km]", breaks = seq(0,30,5)))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#7
seven <- NO3_3rdO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#11
eleven <- NO3_3rdO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#15
fifteen <- NO3_3rdO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab("% of 3rd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)

#4
four <- NO3_4thO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#8
eight <- NO3_4thO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  ylim(0,40)+
  scale_x_continuous(breaks=seq(0,100,by=20))+
        theme(aspect.ratio = 1)
#12
twelve <- NO3_4thO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)
#16
sixteen <- NO3_4thO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pWLR_.5mgL, color = storm), size = 0.2)+
  xlab("% of 4th-order \n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,40)+
        theme(aspect.ratio = 1)


one+theme(text = element_text(size = 5))+
two+theme(text = element_text(size = 5))+
three+theme(text = element_text(size = 5))+
four+theme(text = element_text(size = 5))+
five+theme(text = element_text(size = 5))+
six+theme(text = element_text(size = 5))+
seven+theme(text = element_text(size = 5))+
eight+theme(text = element_text(size = 5))+
nine+theme(text = element_text(size = 5))+
ten+theme(text = element_text(size = 5))+
eleven +theme(text = element_text(size = 5))+ 
twelve +theme(text = element_text(size = 5))+ 
thirteen+theme(text = element_text(size = 5))+
fourteen+theme(text = element_text(size = 5))+
fifteen+theme(text = element_text(size = 5))+
sixteen+theme(text = element_text(size = 5))+
            plot_layout(ncol = 4, guides = "collect")+
            plot_annotation(title = 'Percent NO3 Removed from the Watershed Cumulatively (k90) \n 0.5 mgL source concentration', 
                            theme = theme(title = element_text(size = 8, face = 2)))
ggsave("Exports/SOmatrixWSL_uni_k90.5mgL.png", dpi=500, height=4, width=5, units="in")
# ggsave("Exports/SOmatrixWSL_non_k90.5mgL.png", dpi=500, height=4, width=5, units="in")
```

#Local removal Plots
```{r}
#1
one <- NO3_1stO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("% 1st order NO3 Removed \n by the 1st order Rivers")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "Total Length of 1st-order Rivers Restored [km]", breaks = seq(0,50,10)))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#5
five <-  NO3_1stO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("% 2nd order NO3 Removed \n by the 2nd order Rivers")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#9
nine <-  NO3_1stO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("% 3rd order NO3 Removed \n by 3rd order Rivers")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#13
thirteen <-  NO3_1stO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab("% of 1st-order\n Streams Restored")+
  ylab("% 4th order NO3 Removed \n by the 4th order River")+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)


#2
two <- NO3_2ndO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "Total Length of 2nd-order Rivers Restored [km]", breaks = seq(0,35,5)))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#6
six <- NO3_2ndO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
 ylim(0,4)+
        theme(aspect.ratio = 1)
#10
ten <- NO3_2ndO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#14
fourteen <- NO3_2ndO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab("% of 2nd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)

#3
three <- NO3_3rdO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "Total Length of 3rd-order Rivers Restored [km]", breaks = seq(0,30,5)))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#7
seven <- NO3_3rdO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#11
eleven <- NO3_3rdO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#15
fifteen <- NO3_3rdO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab("% of 3rd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)

#4
four <- NO3_4thO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "Total Length of 4th-order River Restored [km]", breaks = seq(0,35,5)))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#8
eight <- NO3_4thO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#12
twelve <- NO3_4thO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)
#16
sixteen <- NO3_4thO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentOLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentOLR, color = storm), size = 0.2)+
  xlab("% of 4th-order \n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  ylim(0,4)+
        theme(aspect.ratio = 1)

one+theme(text = element_text(size = 5))+
two+theme(text = element_text(size = 5))+
three+theme(text = element_text(size = 5))+
four+theme(text = element_text(size = 5))+
five+theme(text = element_text(size = 5))+
six+theme(text = element_text(size = 5))+
seven+theme(text = element_text(size = 5))+
eight+theme(text = element_text(size = 5))+
nine+theme(text = element_text(size = 5))+
ten+theme(text = element_text(size = 5))+
eleven +theme(text = element_text(size = 5))+ 
twelve +theme(text = element_text(size = 5))+ 
thirteen+theme(text = element_text(size = 5))+
fourteen+theme(text = element_text(size = 5))+
fifteen+theme(text = element_text(size = 5))+
sixteen+theme(text = element_text(size = 5))+
          plot_layout(ncol = 4, guides = "collect")+
          plot_annotation(title = 'Percent NO3 Removed from an Individual Order \n With Respect to the Loading to the Individual Order (km)', 
                          theme = theme(title = element_text(size = 8, face = 2)))
```

```{r}
ggsave("Exports/localRem_matrix_km_uni.png", dpi=500, height=4, width=5, units="in")
#ggsave("Exports/localRem_matrix_km_non.png", dpi=500, height=4, width=5, units="in")
```

##Engineering added benefit plots:
```{r}
NO3_SO <- bind_rows(NO3_1stO, NO3_2ndO, NO3_3rdO, NO3_4thO)%>%
  mutate_if(is.numeric, # Using dplyr functions
            round,
            digits = 3)
NO3_SO$storm <- factor(NO3_SO$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
NO3_SO%>%
  filter(plan == "unr" | plan == "1st-20p" | plan == "1st-40p" | plan == "1st-60p" | plan == "1st-80p" | plan == "1st-100p")%>%
  ggplot()+
  geom_line(aes(percentRest, km_percentWLR, color = storm))+
  geom_point(aes(percentRest, km_percentWLR, color = storm))+
  facet_wrap( ~river, scales = "free", ncol = 2)+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  xlab("% of 1st-order Streams Restored")+
  ylab("%Total Watershed NO3 Removed \n in a Particular River")+
  ggtitle("NO3 Removal Added Benefit from Each Order (km)")
#ggsave("Exports/Isolated_AddedBenefit_km1stO.png", dpi=500, height=4, width=5, units="in")

NO3_SO%>%
  filter(plan == "unr" | plan == "2nd-20p" | plan == "2nd-60p" | plan == "2nd-80p" | plan == "2nd-100p")%>%
  ggplot()+
  geom_line(aes(percentRest, km_percentWLR, color = storm))+
  geom_point(aes(percentRest, km_percentWLR, color = storm))+
  facet_wrap( ~river, scales = "free", ncol = 2)+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  xlab("% of 2nd-order Streams Restored")+
  ylab("%Total Watershed NO3 Removed \n in a Particular River")+
  ggtitle("NO3 Removal Added Benefit from Each Order (km)")
#ggsave("Exports/Isolated_AddedBenefit_km2ndO.png", dpi=500, height=4, width=5, units="in")

NO3_SO%>%
  filter(plan == "unr" | plan == "3rd-20p" | plan == "3rd-40p" | plan == "3rd-60p" | plan == "3rd-80p" | plan == "3rd-100p")%>%
  ggplot()+
  geom_line(aes(percentRest, km_percentWLR, color = storm))+
  geom_point(aes(percentRest, km_percentWLR, color = storm))+
  facet_wrap( ~river, scales = "free", ncol = 2)+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  xlab("% of 3rd-order Streams Restored")+
  ylab("%Total Watershed NO3 Removed \n in a Particular River")+
  ggtitle("NO3 Removal Added Benefit from Each Order (km)")
#ggsave("Exports/Isolated_AddedBenefit_km3rdO.png", dpi=500, height=4, width=5, units="in")

NO3_SO%>%
  filter(plan == "unr" | plan == "4th-20p" | plan == "4th-40p" | plan == "4th-60p" | plan == "4th-80p" | plan == "4th-100p")%>%
  ggplot()+
  geom_line(aes(percentRest, km_percentWLR, color = storm))+
  geom_point(aes(percentRest, km_percentWLR, color = storm))+
  facet_wrap( ~river, scales = "free", ncol = 2)+
  scale_x_continuous(breaks=seq(0,100,by=20))+
  xlab("% of 4th-order Stream Restored")+
  ylab("%Total Watershed NO3 Removed \n in a Particular River")+
  ggtitle("NO3 Removal Added Benefit from Each Order (km)")
#ggsave("Exports/Isolated_AddedBenefit_km4thO.png", dpi=500, height=4, width=5, units="in")

# write_csv(NO3_SO, "Exports/NO3_SO_data.csv")
```


#Added Benefit Matrix
```{r}
#1
one <- NO3_1stO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
   xlab(expression(atop("Percent of 1"^st*"-Order Rivers Restored")))+
   ylab(expression(atop("%NO"[3]*" Removed in 1"^st*"-order rivers")))+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "Tot Length of 1st-order\n Rivers Restored [km]", breaks = seq(0,50,10)))
#5
five <-  NO3_1stO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%Tot Watershed Load Rem. \n by the 2nd order Rivers")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#9
nine <-  NO3_1stO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%Tot Watershed Load Rem.  \n by 3rd order Rivers")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#13
thirteen <-  NO3_1stO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab("% of 1st-order\n Streams Restored")+
  ylab("%Tot Watershed Load Rem.  \n by the 4th order River")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)


#2
two <- NO3_2ndO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "Tot Length of 2nd-order\n Rivers Restored [km]", breaks = seq(0,35,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#6
six <- NO3_2ndO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(expression(atop("Percent of 2"^nd*"-Order Rivers Restored")))+
    ylab(expression(atop("%NO"[3]*" Removed in 2"^nd*"-order rivers")))+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))
#10
ten <- NO3_2ndO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#14
fourteen <- NO3_2ndO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab("% of 2nd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)

#3
three <- NO3_3rdO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "Tot Length of 3rd-order\n Rivers Restored [km]", breaks = seq(0,30,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#7
seven <- NO3_3rdO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#11
eleven <- NO3_3rdO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(expression(atop("Percent of 3"^rd*"-Order Rivers Restored")))+
  ylab(expression(atop("%NO"[3]*" Removed in 3"^rd*"-order rivers")))+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))
#15
fifteen <- NO3_3rdO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab("% of 3rd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)

#4
four <- NO3_4thO %>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "Tot Length of 4th-order\n River Restored [km]", breaks = seq(0,35,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#8
eight <- NO3_4thO %>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#12
twelve <- NO3_4thO %>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))+
  # ylim(0,1)+
        theme(aspect.ratio = 1)
#16
sixteen <- NO3_4thO %>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_percentWLR, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_percentWLR, color = storm), size = 0.2)+
  xlab(expression(atop("Percent of the 4"^th*"-Order River Restored")))+
    ylab(expression(atop("%NO"[3]*" Removed in the 4"^th*"-order river")))+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))

one+theme(text = element_text(size = 5))+
two+theme(text = element_text(size = 5))+
three+theme(text = element_text(size = 5))+
four+theme(text = element_text(size = 5))+
five+theme(text = element_text(size = 5))+
six+theme(text = element_text(size = 5))+
seven+theme(text = element_text(size = 5))+
eight+theme(text = element_text(size = 5))+
nine+theme(text = element_text(size = 5))+
ten+theme(text = element_text(size = 5))+
eleven +theme(text = element_text(size = 5))+ 
twelve +theme(text = element_text(size = 5))+ 
thirteen+theme(text = element_text(size = 5))+
fourteen+theme(text = element_text(size = 5))+
fifteen+theme(text = element_text(size = 5))+
sixteen+theme(text = element_text(size = 5))+
          plot_layout(ncol = 4, guides = "collect")+
          plot_annotation(title = '%Total Watershed Load Removed by an Individual Order (km)', 
                          theme = theme(title = element_text(size = 8, face = 2))) &
  ylim(0,1)
```



```{r}
# ggsave("Exports/EngAddedBenefit_non_km.png", dpi=500, height=4, width=5, units="in")
ggsave("Exports/EngAddedBenefit_uni_km.png", dpi=500, height=5, width=5, units="in")
```

##unrestored removal baseline plot

```{r plot-wider, fig.width=9, fig.height=4}
unr <- rbind(NO3_1stO, NO3_2ndO, NO3_3rdO, NO3_4thO)
unr <- unr%>%
  filter(plan == "unr")%>%
  mutate(Order = case_when(river == "1-7"~"1st-order",
                           river == "2-2"~"2nd-order",
                           river == "3-1"~"3rd-order",
                           river == "4-1"~"4th-order"))
unr$storm <- factor(unr$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
baseline_km <- unr%>%
  ggplot()+
  geom_point(aes(Order, km_percentWLR, color = storm))+
  geom_line(aes(Order, km_percentWLR, group = storm, color = storm))+
  ylim(0,0.15)+
  xlab(element_blank())+
  ylab(element_blank())+
  ggtitle(expression(atop("k"[m])))

baseline_k10 <- unr%>%
  ggplot()+
  geom_point(aes(Order, k10_percentWLR, color = storm))+
  geom_line(aes(Order, k10_percentWLR, group = storm, color = storm))+
  # ylim(0,0.015)+
  xlab(element_blank())+
  ylab("Percent of Total Watershed Load Removed")+
  ggtitle(expression(atop("k"[10])))

baseline_k90 <- unr%>%
  ggplot()+
  geom_point(aes(Order, k90_percentWLR, color = storm))+
  geom_line(aes(Order, k90_percentWLR, group = storm, color = storm))+
  ylim(0,3)+
  xlab(element_blank())+
  ylab(element_blank())+
  ggtitle(expression(atop("k"[90])))

baseline_k10+baseline_km+baseline_k90+ 
  plot_layout(ncol = 3, guides = "collect")+
            plot_annotation(title = expression(atop("Baseline NO"[3]*" Removal: Percent NO"[3]*" Removed from the Unrestored 4"^th*"-order Watershed")), 
                            caption = expression("River Order Location of NO"[3]*" Removal"),
                            theme = theme(title = element_text(size = 10, face = 2), plot.caption = element_text(hjust = 0.5)),
                            tag_levels = 'A')&
  theme(text = element_text(size = 8))

ggsave("Figures/baselineRemoval.png", dpi=500, height = 4, width = 9, units="in")
```

##Baseline removal in different watershed sizes within the 4th-order
```{r}
unr_monitor <- monitorSO%>%
  filter(plan == "unr")%>%
  mutate(Order = case_when(river == "1-7"~"1st-order",
                           river == "2-2"~"2nd-order",
                           river == "3-1"~"3rd-order",
                           river == "4-1"~"4th-order"))
unr_monitor$storm <- factor(unr_monitor$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
# baseline_km <- 
unr_monitor%>%
  ggplot()+
  geom_point(aes(Order, km_pRem, color = storm))+
  geom_line(aes(Order, km_pRem, group = storm, color = storm))+
  # ylim(0,0.15)+
  xlab("Watershed Order")+
  ylab(expression("Percent Watershed NO"[3]*"Load Removed"))+
  ggtitle(expression(atop("Baseline NO"[3]*" Removal:", "Percent NO"[3]*" Removed by Watershed Size (k"[m]*")")))
ggsave("Figures/baselineMonitor.png", dpi=500, height = 3, width = 6, units="in")
# baseline_k10 <- unr_monitor%>%
#   ggplot()+
#   geom_point(aes(Order, km_pRem, color = storm))+
#   geom_line(aes(Order, km_pRem, group = storm, color = storm))+
#   # ylim(0,0.015)+
#   xlab(element_blank())+
#   ylab("Percent Watershed NO"[3]*"Load Removed")+
#   ggtitle(expression(atop("k"[10])))
# 
# baseline_k90 <- unr_monitor%>%
#   ggplot()+
#   geom_point(aes(Order, km_pRem, color = storm))+
#   geom_line(aes(Order, km_pRem, group = storm, color = storm))+
#   # ylim(0,3)+
#   xlab(element_blank())+
#   ylab(element_blank())+
#   ggtitle(expression(atop("k"[90])))
# 
# baseline_k10+baseline_km+baseline_k90+ 
#   plot_layout(ncol = 3, guides = "collect")+
#             plot_annotation(title = expression(atop("Baseline NO"[3]*" Removal: Percent NO"[3]*" Removed by Watershed Size")), 
#                             caption = expression("Watershed Order"),
#                             theme = theme(title = element_text(size = 10, face = 2), plot.caption = element_text(hjust = 0.5)),
#                             tag_levels = 'A')&
#   theme(text = element_text(size = 8))

```


#Outlet Plots:
```{r plot-wider, fig.width=16, fig.height=11}
#make sure to run individual order removal matrix
outlet_1stO <- NO3_1stO %>%
  group_by(storm,plan)%>%
  summarise(km_Premoval = sum(km_percentWLR), k90_Premoval = sum(k90_percentWLR), k10_Premoval = sum(k10_percentWLR), 
            km_pWLR_2mgL =    sum(km_pWLR_2mgL), k90_pWLR_2mgL = sum(k90_pWLR_2mgL), k10_pWLR_2mgL = sum(k10_pWLR_2mgL), 
            km_pWLR_.5mgL = sum(km_pWLR_.5mgL), k90_pWLR_.5mgL = sum(k90_pWLR_.5mgL), k10_pWLR_.5mgL = sum(k10_pWLR_.5mgL))%>%
   mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0)) %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_Premoval, color = storm),linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_Premoval, color = storm), size = 0.2)+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = expression(atop("Total Length of 1"^st*"-order Rivers Restored [km]")), breaks = seq(0,50,10)))+
  xlab(element_blank())+
  ylim(0,0.2)+
  ylab(expression("% NO"[3]* " Removed from the Watershed"))
  
outlet_2ndO <- NO3_2ndO %>% 
    group_by(storm,plan)%>%
    summarise(km_Premoval = sum(km_percentWLR), k90_Premoval = sum(k90_percentWLR), k10_Premoval = sum(k10_percentWLR), 
              km_pWLR_2mgL = sum(km_pWLR_2mgL), k90_pWLR_2mgL = sum(k90_pWLR_2mgL), k10_pWLR_2mgL = sum(k10_pWLR_2mgL), 
              km_pWLR_.5mgL = sum(km_pWLR_.5mgL), k90_pWLR_.5mgL = sum(k90_pWLR_.5mgL), k10_pWLR_.5mgL = sum(k10_pWLR_.5mgL))%>%
    mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0)) %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_Premoval, color = storm),linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_Premoval, color = storm), size = 0.2)+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = expression(atop("Total Length of 2"^nd*"-order Rivers Restored [km]")), breaks = seq(0,35,5)))+
  xlab(element_blank())+
    ylim(0,0.25)+
  ylab(expression("% NO"[3]* " Removed from the Watershed"))
  
outlet_3rdO <- NO3_3rdO %>%
  group_by(storm,plan)%>%
  summarise(km_Premoval = sum(km_percentWLR), k90_Premoval = sum(k90_percentWLR), k10_Premoval = sum(k10_percentWLR), 
            km_pWLR_2mgL = sum(km_pWLR_2mgL), k90_pWLR_2mgL = sum(k90_pWLR_2mgL), k10_pWLR_2mgL = sum(k10_pWLR_2mgL), 
            km_pWLR_.5mgL = sum(km_pWLR_.5mgL), k90_pWLR_.5mgL = sum(k90_pWLR_.5mgL), k10_pWLR_.5mgL = sum(k10_pWLR_.5mgL))%>%
    mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0)) %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_Premoval, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_Premoval, color = storm), size = 0.2)+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = expression(atop("Total Length of 3"^rd*"-order Rivers Restored [km]")), breaks = seq(0,30,5)))+
  xlab(element_blank())+
  ylim(0,0.3)+
  ylab(expression("% NO"[3]* " Removed from the Watershed"))
   
outlet_4th <- NO3_4thO %>% 
  group_by(storm,plan)%>%
  summarise(km_Premoval = sum(km_percentWLR), k90_Premoval = sum(k90_percentWLR), k10_Premoval = sum(k10_percentWLR), 
            km_pWLR_2mgL = sum(km_pWLR_2mgL), k90_pWLR_2mgL = sum(k90_pWLR_2mgL), k10_pWLR_2mgL = sum(k10_pWLR_2mgL), 
            km_pWLR_.5mgL = sum(km_pWLR_.5mgL), k90_pWLR_.5mgL = sum(k90_pWLR_.5mgL), k10_pWLR_.5mgL = sum(k10_pWLR_.5mgL))%>%
  mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0)) %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_Premoval, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = km_Premoval, color = storm), size = 0.2)+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = expression(atop("Total Length of 4"^th*"-order Rivers Restored [km]")), breaks = seq(0,35,5)))+
  ylim(0,1)+
  xlab(element_blank())+
  ylab(expression("% NO"[3]* " Removed from the Watershed"))

outlet_1stO+ outlet_2ndO+ outlet_3rdO+ outlet_4th+
one+
   ylim(0,0.2)+
   scale_x_continuous(sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))+
six+
   ylim(0,0.25)+
   scale_x_continuous(sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))+
eleven+
   ylim(0,0.3)+
   scale_x_continuous(sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))+
sixteen+
   ylim(0,1)+
   scale_x_continuous(sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))+
plot_layout(
  ncol = 4, 
  guides = "collect")+
plot_annotation(
  title = expression(atop("4"^th*" order Watershed NO"[3]*" Removal vs a River Order NO"[3]*" Removal (k"[m]*" rate)")),
  tag_levels = list(c("A", "", "", "", "B", "", "", "")),
  theme = theme(title = element_text(size = 12, face = 2))) &
theme(text = element_text(size = 10))

ggsave("Figures/WatershedvsOrderRemoval_km.png", dpi=500,width = 15, height = 7, units="in")
```

```{r plot-wider, fig.width=16, fig.height=11}
#make sure to run individual order removal matrix
outlet_1stO <- NO3_1stO %>%
  group_by(storm,plan)%>%
  summarise(km_Premoval = sum(km_percentWLR), k90_Premoval = sum(k90_percentWLR), k10_Premoval = sum(k10_percentWLR), 
            km_pWLR_2mgL =    sum(km_pWLR_2mgL), k90_pWLR_2mgL = sum(k90_pWLR_2mgL), k10_pWLR_2mgL = sum(k10_pWLR_2mgL), 
            km_pWLR_.5mgL = sum(km_pWLR_.5mgL), k90_pWLR_.5mgL = sum(k90_pWLR_.5mgL), k10_pWLR_.5mgL = sum(k10_pWLR_.5mgL))%>%
   mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0)) %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_Premoval, color = storm),linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_Premoval, color = storm), size = 0.2)+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = expression(atop("Total Length of 1"^st*"-order Rivers Restored [km]")), breaks = seq(0,50,10)))+
  xlab(element_blank())+
  ylim(0,4)+
  ylab(expression("% NO"[3]* " Removed from the Watershed"))
  
outlet_2ndO <- NO3_2ndO %>% 
    group_by(storm,plan)%>%
    summarise(km_Premoval = sum(km_percentWLR), k90_Premoval = sum(k90_percentWLR), k10_Premoval = sum(k10_percentWLR), 
              km_pWLR_2mgL = sum(km_pWLR_2mgL), k90_pWLR_2mgL = sum(k90_pWLR_2mgL), k10_pWLR_2mgL = sum(k10_pWLR_2mgL), 
              km_pWLR_.5mgL = sum(km_pWLR_.5mgL), k90_pWLR_.5mgL = sum(k90_pWLR_.5mgL), k10_pWLR_.5mgL = sum(k10_pWLR_.5mgL))%>%
    mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0)) %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_Premoval, color = storm),linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_Premoval, color = storm), size = 0.2)+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = expression(atop("Total Length of 2"^nd*"-order Rivers Restored [km]")), breaks = seq(0,35,5)))+
  xlab(element_blank())+
    ylim(0,5)+
  ylab(expression("% NO"[3]* " Removed from the Watershed"))
  
outlet_3rdO <- NO3_3rdO %>%
  group_by(storm,plan)%>%
  summarise(km_Premoval = sum(km_percentWLR), k90_Premoval = sum(k90_percentWLR), k10_Premoval = sum(k10_percentWLR), 
            km_pWLR_2mgL = sum(km_pWLR_2mgL), k90_pWLR_2mgL = sum(k90_pWLR_2mgL), k10_pWLR_2mgL = sum(k10_pWLR_2mgL), 
            km_pWLR_.5mgL = sum(km_pWLR_.5mgL), k90_pWLR_.5mgL = sum(k90_pWLR_.5mgL), k10_pWLR_.5mgL = sum(k10_pWLR_.5mgL))%>%
    mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0)) %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_Premoval, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_Premoval, color = storm), size = 0.2)+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = expression(atop("Total Length of 3"^rd*"-order Rivers Restored [km]")), breaks = seq(0,30,5)))+
  xlab(element_blank())+
  ylim(0,6)+
  ylab(expression("% NO"[3]* " Removed from the Watershed"))
   
outlet_4th <- NO3_4thO %>% 
  group_by(storm,plan)%>%
  summarise(km_Premoval = sum(km_percentWLR), k90_Premoval = sum(k90_percentWLR), k10_Premoval = sum(k10_percentWLR), 
            km_pWLR_2mgL = sum(km_pWLR_2mgL), k90_pWLR_2mgL = sum(k90_pWLR_2mgL), k10_pWLR_2mgL = sum(k10_pWLR_2mgL), 
            km_pWLR_.5mgL = sum(km_pWLR_.5mgL), k90_pWLR_.5mgL = sum(k90_pWLR_.5mgL), k10_pWLR_.5mgL = sum(k10_pWLR_.5mgL))%>%
  mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0)) %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = k90_Premoval, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_Premoval, color = storm), size = 0.2)+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = expression(atop("Total Length of 4"^th*"-order Rivers Restored [km]")), breaks = seq(0,35,5)))+
  ylim(0,20)+
  xlab(element_blank())+
  ylab(expression("% NO"[3]* " Removed from the Watershed"))

outlet_1stO+ outlet_2ndO+ outlet_3rdO+ outlet_4th+
one+
   ylim(0,4)+
   scale_x_continuous(sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))+
six+
   ylim(0,5)+
   scale_x_continuous(sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))+
eleven+
   ylim(0,6)+
   scale_x_continuous(sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))+
sixteen+
   ylim(0,20)+
   scale_x_continuous(sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))+
plot_layout(
  ncol = 4, 
  guides = "collect")+
plot_annotation(
  title = expression(atop("4"^th*" order Watershed NO"[3]*" Removal vs a River Order NO"[3]*" Removal (k"[90]*" rate)")),
  tag_levels = list(c("A", "", "", "", "B", "", "", "")),
  theme = theme(title = element_text(size = 12, face = 2))) &
theme(text = element_text(size = 10))

  ggsave("Figures/WatershedvsOrderRemoval_k90.png", dpi=500,width = 15, height = 7, units="in")
```


#Plots representing the removal that would be observed if were monitoring DS of 1 watershed order
```{r}
# NO3_4thO <- NO3_4thO[!NO3_4thO$plan == "unr", ]

#Nitrate loads for 1mg/L source concentration(g)
Q2_watershed_load <- 4563108 #total NO3 load to the watershed (grams)
Q2_load1 <- 141902 #input load to a all first order streams (grams)
Q2_load2 <- 120581 #input load to a all second order streams (grams)
Q2_load3 <- 680432 #input load to a all third order streams (grams)
Q2_load4 <- 3620193 #input load to the fourth order stream (grams)

Q1_watershed_load <- 3653361 #total NO3 load to the watershed (grams)
Q1_load1 <- 102974 #input load to a all first order streams (grams)
Q1_load2 <- 126125 #input load to a all second order streams (grams)
Q1_load3 <- 545822 #input load to a all third order streams (grams)
Q1_load4 <- 2878440 #input load to the fourth order stream (grams)

Q0.5_watershed_load <- 2262609 #total NO3 load to the watershed (grams)
Q0.5_load1 <- 91515 #input load to a all first order streams (grams)
Q0.5_load2 <- 74539 #input load to a all second order streams (grams)
Q0.5_load3 <- 325804 #input load to a all third order streams (grams)
Q0.5_load4 <- 1770751 #input load to the fourth order stream (grams)

Qm_watershed_load <- 245161 #total NO3 load to the watershed (grams)
Qm_load1 <- 65880 #input load to a all first order streams (grams)
Qm_load2 <- 3003 #input load to a all second order streams (grams)
Qm_load3 <- 26865 #input load to a all third order streams (grams)
Qm_load4 <- 149414 #input load to the fourth order stream (grams)

monitorSO <- monitorSO %>% #bind_rows(NO3_1stO, NO3_2ndO, NO3_3rdO, NO3_4thO)%>% #NO3 removals here are from 1 river of each order
  #1st order watershed monitor will be just filtering for river 1-7. Represents removal from one 1st order.
  #2nd order watershed monitoring will be (1-7)*4 + (2-2)
  #3rd order watershed monitoring will be ^ *3 + (3-1)
  #4th order watershed monitoring will be ^ *2
  #cumulatively summing removal at each order outlet. The load removed from a single order is the load associated with that order outlet column and river.
  mutate(secOutlet = case_when(river == "1-7" ~ removal_k90_g*4,
                               river == "2-2" ~ removal_k90_g),
         secOutlet = ave(secOutlet, storm, plan, FUN = cumsum),
         thirOutlet = case_when(river == "1-7" ~ removal_k90_g*12,
                                river == "2-2" ~ removal_k90_g*3,
                                river == "3-1" ~ removal_k90_g),
         thirOutlet = ave(thirOutlet, storm, plan, FUN = cumsum),
         fourOutlet = case_when(river == "1-7" ~ removal_k90_g*24,
                                river == "2-2" ~ removal_k90_g*6,
                                river == "3-1" ~ removal_k90_g*2,
                                river == "4-1" ~ removal_k90_g),
         fourOutlet = ave(fourOutlet, storm, plan, FUN = cumsum))%>%
  group_by(storm, plan)%>%
  #percent removal by watershed order
  mutate(k90_pRem = 
           case_when(river == "1-7" & storm == "Q2" ~ (removal_k90_g/(Q2_load1/24))*100,
                     river == "1-7" & storm == "Q1" ~ (removal_k90_g/(Q1_load1/24))*100,
                     river == "1-7" & storm == "Q0.5" ~ (removal_k90_g/(Q0.5_load1/24))*100,
                     river == "1-7" & storm == "Qm" ~ (removal_k90_g/(Qm_load1/24))*100,
                     river == "2-2" & storm == "Q2" ~ (secOutlet/((Q2_load1/6)+(Q2_load2/6)))*100,
                     river == "2-2" & storm == "Q1" ~ (secOutlet/((Q1_load1/6)+(Q1_load2/6)))*100,
                     river == "2-2" & storm == "Q0.5" ~ (secOutlet/((Q0.5_load1/6)+(Q0.5_load2/6)))*100,
                     river == "2-2" & storm == "Qm" ~ (secOutlet/((Qm_load1/6)+(Qm_load2/6)))*100,
                     river == "3-1" & storm == "Q2" ~ (thirOutlet/((Q2_load1/2)+(Q2_load2/2)+(Q2_load3/2)))*100,
                     river == "3-1" & storm == "Q1" ~ (thirOutlet/((Q1_load1/2)+(Q1_load2/2)+(Q1_load3/2)))*100,
                     river == "3-1" & storm == "Q0.5" ~ (thirOutlet/((Q0.5_load1/2)+(Q0.5_load2/2)+(Q0.5_load3/2)))*100,
                     river == "3-1" & storm == "Qm" ~ (thirOutlet/((Qm_load1/2)+(Qm_load2/2)+(Qm_load3/2)))*100,
                     river == "4-1" & storm == "Q2" ~ (fourOutlet/Q2_watershed_load)*100,
                     river == "4-1" & storm == "Q1" ~ (fourOutlet/Q1_watershed_load)*100,
                     river == "4-1" & storm == "Q0.5" ~ (fourOutlet/Q0.5_watershed_load)*100,
                     river == "4-1" & storm == "Qm" ~ (fourOutlet/Qm_watershed_load)*100))%>%
   mutate(restLoc = 
           case_when(startsWith(plan, "unr") ~ "unr",
                     startsWith(plan, "1st") ~ "1st",
                     startsWith(plan, "2nd") ~ "2nd",
                     startsWith(plan, "3rd") ~ "3rd",
                     startsWith(plan, "4th") ~ "4th"))%>% 
  mutate(percentRest = case_when(endsWith(plan, "100p")~ 100,
                                 endsWith(plan, "80p")~ 80,
                                 endsWith(plan, "60p")~ 60,
                                 endsWith(plan, "40p")~ 40,
                                 endsWith(plan, "20p")~ 20,
                                 endsWith(plan, "unr")~ 0))

# save(monitorSO,
#      file = "C:/Users/morganao/Documents/CBT_Oehler2023/9_Saved_Dataframes/monitorSO.RData")

```

#km
```{r plot-wider, fig.width=10, fig.height=10}
monitorSO$storm <- factor(monitorSO$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
#1
one <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "1st")%>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(expression(atop("%NO"[3]*" Removed from", "a 1"^st*"-order Watershed")))+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "Tot Length of 1st-order\n Rivers Restored [km]", breaks = seq(0,50,10)))
#5
five <-  monitorSO %>%
  filter(restLoc == "unr" | restLoc == "1st")%>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(expression(atop("%NO"[3]*" Removed from", "a 2"^nd*"-order Watershed")))+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))
#9
nine <-  monitorSO %>%
  filter(restLoc == "unr" | restLoc == "1st")%>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(expression(atop("%NO"[3]*" Removed from", "a 3"^rd*"-order Watershed")))+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))
#13
thirteen <-  monitorSO %>%
  filter(restLoc == "unr" | restLoc == "1st")%>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(expression(atop("Percent of 1"^st*"-Order", "Rivers Restored")))+
  ylab(expression(atop("%NO"[3]*" Removed from", "the 4"^th*"-order Watershed")))+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))


#2
two <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "2nd")%>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "Tot Length of 2nd-order\n Rivers Restored [km]", breaks = seq(0,35,5)))
#6
six <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "2nd")%>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))
#10
ten <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "2nd")%>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))
#14
fourteen <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "2nd")%>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(expression(atop("Percent of 2"^nd*"-Order", " Rivers Restored")))+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))

#3
three <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "3rd")%>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "Tot Length of 3rd-order\n Rivers Restored [km]", breaks = seq(0,30,5)))
#7
seven <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "3rd")%>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))
#11
eleven <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "3rd")%>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))
#15
fifteen <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "3rd")%>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(expression(atop("Percent of 3"^rd*"-Order", " Rivers Restored")))+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))

#4
four <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "4th")%>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "Tot Length of 4th-order\n River Restored [km]", breaks = seq(0,35,5)))
#8
eight <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "4th")%>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))
#12
twelve <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "4th")%>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))
#16
sixteen <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "4th")%>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y = km_pRem, color = storm), linewidth = 0.8)+
  geom_point(aes(x = percentRest, y = km_pRem, color = storm), size = 0.5)+
  xlab(expression(atop("Percent of 4"^th*"-Order", " River Restored")))+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))

one+two+three+four+five+six+seven+eight+nine+ten+eleven+twelve+thirteen+fourteen+fifteen+sixteen+
  plot_layout(ncol = 4, guides = "collect")+
  plot_annotation(title = expression("%NO"[3]*" Load Removed by Watershed Order"), 
                  subtitle = "Median removal rate, 1mgL background concentration ",
                  theme = theme(title = element_text(size = 12, face = 2))) &
   ylim(0,1) &
  theme(text = element_text(size = 10))

ggsave("Figures/monitoring_km_uni.png", dpi=500, units="in")
```

#k90
```{r}
monitorSO$storm <- factor(monitorSO$storm,                 # Re-level group factor
                         levels = c("Q2", "Q1", "Q0.5", "Qm"))
#1
one <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "1st")%>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed from\n a 1st-order Watershed")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "Tot Length of 1st-order\n Rivers Restored [km]", breaks = seq(0,50,10)))+
  theme(aspect.ratio = 1)
#5
five <-  monitorSO %>%
  filter(restLoc == "unr" | restLoc == "1st")%>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed from\n a 2nd-order Watershed")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))+
  theme(aspect.ratio = 1)
#9
nine <-  monitorSO %>%
  filter(restLoc == "unr" | restLoc == "1st")%>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab("%NO3 Removed from\n a 3rd-order Watershed")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))+
  theme(aspect.ratio = 1)
#13
thirteen <-  monitorSO %>%
  filter(restLoc == "unr" | restLoc == "1st")%>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab("% of 1st-order\n Streams Restored")+
  ylab("%NO3 Removed from\n a 4th-order Watershed")+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.43891, name = "", breaks = seq(0,50,10)))+
  theme(aspect.ratio = 1)


#2
two <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "2nd")%>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "Tot Length of 2nd-order\n Rivers Restored [km]", breaks = seq(0,35,5)))+
  theme(aspect.ratio = 1)
#6
six <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "2nd")%>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))+
  theme(aspect.ratio = 1)
#10
ten <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "2nd")%>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))+
  theme(aspect.ratio = 1)
#14
fourteen <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "2nd")%>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab("% of 2nd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30175, name = "", breaks = seq(0,35,5)))+
  theme(aspect.ratio = 1)

#3
three <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "3rd")%>%
  filter(river == "1-7") %>%
  ggplot()+
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "Tot Length of 3rd-order\n Rivers Restored [km]", breaks = seq(0,30,5)))+
  theme(aspect.ratio = 1)
#7
seven <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "3rd")%>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))+
  theme(aspect.ratio = 1)
#11
eleven <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "3rd")%>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))+
  theme(aspect.ratio = 1)
#15
fifteen <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "3rd")%>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab("% of 3rd-order\n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.25603, name = "", breaks = seq(0,30,5)))+
  theme(aspect.ratio = 1)

#4
four <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "4th")%>%
  filter(river == "1-7") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "Tot Length of 4th-order\n River Restored [km]", breaks = seq(0,35,5)))+
  theme(aspect.ratio = 1)
#8
eight <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "4th")%>%
  filter(river == "2-2") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))+
  theme(aspect.ratio = 1)
#12
twelve <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "4th")%>%
  filter(river == "3-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab(element_blank())+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))+
  theme(aspect.ratio = 1)
#16
sixteen <- monitorSO %>%
  filter(restLoc == "unr" | restLoc == "4th")%>%
  filter(river == "4-1") %>%
  ggplot() +
  geom_line(aes(x = percentRest, y =  k90_pRem, color = storm), linewidth = 0.5)+
  geom_point(aes(x = percentRest, y = k90_pRem, color = storm), size = 0.2)+
  xlab("% of 4th-order \n Streams Restored")+
  ylab(element_blank())+
  scale_x_continuous(breaks=seq(0,100,by=20),  sec.axis = sec_axis(~. * 0.30785, name = "", breaks = seq(0,35,5)))+
  theme(aspect.ratio = 1)

one+  theme(text =    element_text(size = 4))+
two+  theme(text =    element_text(size = 4))+
three+theme(text =    element_text(size = 4))+
four+ theme(text =    element_text(size = 4))+
five+ theme(text =    element_text(size = 4))+
six+  theme(text =    element_text(size = 4))+
seven+theme(text =    element_text(size = 4))+
eight+theme(text =    element_text(size = 4))+
nine+ theme(text =    element_text(size = 4))+
ten+  theme(text =    element_text(size = 4))+
eleven +theme(text =  element_text(size = 4))+ 
twelve +theme(text =  element_text(size = 4))+ 
thirteen+theme(text = element_text(size = 4))+
fourteen+theme(text = element_text(size = 4))+
fifteen+theme(text =  element_text(size = 4))+
sixteen+theme(text =  element_text(size = 4))+
          plot_layout(ncol = 4, guides = "collect")+
          plot_annotation(title = '%NO3 Load Removed by Watershed Order', 
                          subtitle = "90th Percentile removal rate, 1mgL background concentration ",
                          theme = theme(title = element_text(size = 8, face = 2))) &
    ylim(0,20)

ggsave("Exports/monitoring_k90_uni.png", dpi=500, units="in")
```
