---
title: "HECRAS Output Data Frequency Analysis"
output: html_document
date: "2023-05-18"
---
###Frequency analysis conducted on 100% watershed restoration for a Q1, Qmonth, and Q0.5 storm
#Housekeeping:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(dplyr)
library(tidyverse)
library(stringr)
library(tidyr)
```

#Constants
```{r}
watershed_load <- 3653361 #total NO3 load to the watershed (grams)
load1 <- 102974 #input load to a all first order streams (grams)
load2 <- 126125 #input load to a all second order streams (grams)
load3 <- 545822 #input load to a all third order streams (grams)
load4 <- 2878440 #input load to the fourth order stream (grams)

k <- 0.067 #0.0067 10th percentile
#1.3 90th percentile actual rate from database (mg-N/ft2-hr) #12.08 max from EST paper  #15.97 max actual from database #0.061 median actual from database #0.8178  median potential from database
Xcs <- 50 #Distance between cross sections (ft)


#w_1stO <- 60 #width of one 1st order floodplain (ft)
#w_2ndO <- 65 #width of one 2nd order floodplain (ft)
#w_3rdO <- 75 #width of one 3rd order floodplain (ft)
#w_4thO <- 130 #width of one 4th order floodplain (ft)


```

#Q1
##FIRST ORDERS:
###6-min data output frequency
```{r}
R17_6min_Q1 <- read_csv("FrequencyData/1_7_6min_Q1_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_1stO ~ 6)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(165500,159500) ~ (ti_tot_min/60)*(Xcs/2)*(w_1stO*2)*k/1000,
                                               TRUE ~ (ti_tot_min/60)*Xcs*(w_1stO*2)*k/1000))

Removal17_6min_Q1 <- R17_6min_Q1 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*24)/watershed_load)*100,
    storm = "Q1",
    river = "1_7", 
    data_freq = "6min")

```

###10-min data output frequency
```{r}
R17_10min_Q1 <- read_csv("FrequencyData/1_7_10min_Q1_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_1stO ~ 10)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% 
  mutate(
    removal_g = case_when(STA %in% c(165500, 159500) ~ (ti_tot_min/60)*(Xcs/2)*(w_1stO*2)*k/1000,
                                    TRUE ~ (ti_tot_min/60)*Xcs*(w_1stO*2)*k/1000))

Removal17_10min_Q1 <- R17_10min_Q1 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*24)/watershed_load)*100,
    storm = "Q1",
    river = "1_7", 
    data_freq = "10min")
```

###15-min data output frequency
```{r}
R17_15min_Q1 <- read_csv("FrequencyData/1_7_15min_Q1_full4th100p.csv") %>%
  mutate(sta = 
           case_when(
             endsWith(STA, ".*") ~ substr(STA, 1, nchar(STA)-2), 
             TRUE ~ STA))%>%
  group_by(sta) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_1stO ~ 15)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% 
  mutate(
    removal_g = case_when(sta %in% c(165500, 159500) ~ (ti_tot_min/60)*(Xcs/2)*(w_1stO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_1stO*2)*k/1000))

Removal17_15min_Q1 <- R17_15min_Q1 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*24)/watershed_load)*100,
    storm = "Q1",
    river = "1_7", 
    data_freq = "15min")
```

##SECOND ORDER:
###6-min data output frequency
```{r}
R22_6min_Q1 <- read_csv("FrequencyData/2_2_6min_Q1_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_2ndO ~ 6))%>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(159500, 154000, 148500, 143000) ~ (ti_tot_min/60)*(Xcs/2)*(w_2ndO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_2ndO*2)*k/1000)) #all other XS have normal spacing  

Removal22_6min_Q1 <- R22_6min_Q1 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*6)/watershed_load)*100,
    storm = "Q1",
    river = "2_2", 
    data_freq = "6min")
```

###10-min data output frequency
```{r}
#10 minute data frequency
R22_10min_Q1 <- read_csv("FrequencyData/2_2_10min_Q1_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_2ndO ~ 10))%>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(159500, 154000, 148500, 143000) ~ (ti_tot_min/60)*(Xcs/2)*(w_2ndO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_2ndO*2)*k/1000)) #all other XS have normal spacing  

Removal22_10min_Q1 <- R22_10min_Q1 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*6)/watershed_load)*100,
    storm = "Q1",
    river = "2_2", 
    data_freq = "10min")
```

###15-min data output frequency
```{r}
#15 minute data frequency
R22_15min_Q1 <- read_csv("FrequencyData/2_2_15min_Q1_full4th100p.csv") %>%
  mutate(sta = 
           case_when(
             endsWith(STA, ".*") ~ substr(STA, 1, nchar(STA)-2), 
             TRUE ~ STA))%>%
  group_by(sta) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_2ndO ~ 15))%>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(sta %in% c(159500, 154000, 148500, 143000) ~ (ti_tot_min/60)*(Xcs/2)*(w_2ndO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_2ndO*2)*k/1000)) #all other XS have normal spacing 

Removal22_15min_Q1 <- R22_15min_Q1 %>%
  summarise(
    totalRemoval_g = sum(removal_g))%>%
  mutate(
    percent_removed = ((totalRemoval_g*6)/watershed_load)*100,
    storm = "Q1",
    river = "2_2", 
    data_freq = "15min")
```

##THIRD ORDERS:
###15-min data output frequency
```{r}
R31_15min_Q1 <- read_csv("FrequencyData/3_1_15min_Q1_full4th100p.csv") %>%
  mutate(sta = 
           case_when(
             endsWith(STA, ".*") ~ substr(STA, 1, nchar(STA)-2), 
             TRUE ~ STA)) %>%
  group_by(sta) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_3rdO ~ 15)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>%
  mutate(
    removal_g = case_when(sta %in% c(143000, 122000,  101000) ~ (ti_tot_min/60)*(Xcs/2)*(w_3rdO*2)*k/1000,
                                    TRUE ~ (ti_tot_min/60)*Xcs*(w_3rdO*2)*k/1000))

Removal31_15min_Q1 <- R31_15min_Q1 %>%
  summarise(
    totalRemoval_g = sum(removal_g))%>%
  mutate(
    percent_removed = ((totalRemoval_g*2)/watershed_load)*100,
    storm = "Q1",
    river = "3_1", 
    data_freq = "15min")
  
#write.csv(river31_15min, file = "Exports/river31_15min_Q1.csv")
```

##FOURTH ORDERS:
###15-min data output frequency
```{r}
R41_15min_Q1 <- read_csv("FrequencyData/4_1_15min_Q1_full4th100p.csv") %>%
    mutate(sta = 
           case_when(
             endsWith(STA, ".*") ~ substr(STA, 1, nchar(STA)-2),
             endsWith(STA, ".0*") ~ substr(STA, 1, nchar(STA)-3),
             endsWith(STA, ".00*") ~ substr(STA, 1, nchar(STA)-4),
             TRUE ~ STA)) %>%
  group_by(sta) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_4thO ~ 15)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>%
  mutate(
    removal_g = case_when(sta %in% c(101000, 0) ~ (ti_tot_min/60)*(Xcs/2)*(w_4thO*2)*k/1000,
                           TRUE ~ (ti_tot_min/60)*Xcs*(w_4thO*2)*k/1000))

#cleanup. Don't know why the stations wont go in order automatically, probably bc they're a characters instead of numbers
R41_15min_Q1$sta <-  as.numeric(R41_15min_Q1$sta)
R41_15min_Q1 <- R41_15min_Q1[order(R41_15min_Q1$sta, decreasing = TRUE),]

Removal41_15min_Q1 <- R41_15min_Q1 %>%
  summarise(
    totalRemoval_g = sum(removal_g))%>%
  mutate(
    percent_removed = (totalRemoval_g/watershed_load)*100,
    storm = "Q1",
    river = "4_1", 
    data_freq = "15min")

#write.csv(river41_15min, file = "Exports/river41_15min.csv")

Q1_freq_removal <- rbind(Removal17_6min_Q1, Removal17_10min_Q1, Removal17_15min_Q1,
                        Removal22_6min_Q1, Removal22_10min_Q1, Removal22_15min_Q1,
                        Removal31_15min_Q1,
                        Removal41_15min_Q1) %>%                   
  mutate_if(is.numeric, # Using dplyr functions
            round,
            digits = 3)
```

#Q0.5
##FIRST ORDER:
###5-min data output frequency
```{r}
R17_5min_Q0.5 <- read_csv("FrequencyData/1_7_5min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_1stO ~ 5)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(165500,159500) ~ (ti_tot_min/60)*(Xcs/2)*(w_1stO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_1stO*2)*k/1000))

Removal17_5min_Q0.5 <- R17_5min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*24)/watershed_load)*100,
    storm = "Q0.5",
    river = "1_7", 
    data_freq = "5min") 

```

###10-min data output frequency
```{r}
R17_10min_Q0.5 <- read_csv("FrequencyData/1_7_10min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_1stO ~ 10)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(165500, 159500) ~ (ti_tot_min/60)*(Xcs/2)*(w_1stO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_1stO*2)*k/1000))

Removal17_10min_Q0.5 <- R17_10min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*24)/watershed_load)*100,
    storm = "Q0.5",
    river = "1_7", 
    data_freq = "10min")
```

###15-min data output frequency
```{r}
R17_15min_Q0.5 <- read_csv("FrequencyData/1_7_15min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_1stO ~ 15)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(165500, 159500) ~ (ti_tot_min/60)*(Xcs/2)*(w_1stO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_1stO*2)*k/1000))

Removal17_15min_Q0.5 <- R17_15min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*24)/watershed_load)*100,
    storm = "Q0.5",
    river = "1_7", 
    data_freq = "15min")
```

##SECOND ORDER:
###5-min data output frequency
```{r}
R22_5min_Q0.5 <- read_csv("FrequencyData/2_2_5min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_2ndO ~ 5))%>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(159500, 154000, 148500, 143000) ~ (ti_tot_min/60)*(Xcs/2)*(w_2ndO*2)*k/1000, 
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_2ndO*2)*k/1000)) #all other XS have normal spacing 

Removal22_5min_Q0.5 <- R22_5min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*6)/watershed_load)*100,
    storm = "Q0.5",
    river = "2_2", 
    data_freq = "5min")
```

###10-min data output frequency
```{r}
R22_10min_Q0.5 <- read_csv("FrequencyData/2_2_10min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_2ndO ~ 10))%>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(159500, 154000, 148500, 143000) ~ (ti_tot_min/60)*(Xcs/2)*(w_2ndO*2)*k/1000, 
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_2ndO*2)*k/1000)) #all other XS have normal spacing 

Removal22_10min_Q0.5 <- R22_10min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*6)/watershed_load)*100,
    storm = "Q0.5",
    river = "2_2", 
    data_freq = "10min")
```

###15-min data output frequency
```{r}
R22_15min_Q0.5 <- read_csv("FrequencyData/2_2_15min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_2ndO ~ 15))%>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(159500, 154000, 148500, 143000) ~ (ti_tot_min/60)*(Xcs/2)*(w_2ndO*2)*k/1000, 
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_2ndO*2)*k/1000)) #all other XS have normal spacing 
 
Removal22_15min_Q0.5 <- R22_15min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*6)/watershed_load)*100,
    storm = "Q0.5",
    river = "2_2", 
    data_freq = "15min")
```

##THIRD ORDER:
###5-min data output frequency
```{r}
R31_5min_Q0.5 <- read_csv("FrequencyData/3_1_5min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_3rdO ~ 5)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>%
  mutate(
    removal_g = case_when(STA %in% c(143000, 101000) ~ (ti_tot_min/60)*(Xcs/2)*(w_3rdO*2)*k/1000,
                                    TRUE ~ (ti_tot_min/60)*Xcs*(w_3rdO*2)*k/1000))

Removal31_5min_Q0.5 <- R31_5min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g))%>%
  mutate(
    percent_removed = ((totalRemoval_g*2)/watershed_load)*100,
    storm = "Q0.5",
    river = "3_1", 
    data_freq = "5min")
```

###10-min data output frequency
```{r}
R31_10min_Q0.5 <- read_csv("FrequencyData/3_1_10min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_3rdO ~ 10)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>%
  mutate(
    removal_g = case_when(STA %in% c(143000, 101000) ~ (ti_tot_min/60)*(Xcs/2)*(w_3rdO*2)*k/1000,
                                    TRUE ~ (ti_tot_min/60)*Xcs*(w_3rdO*2)*k/1000))

Removal31_10min_Q0.5 <- R31_10min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g))%>%
  mutate(
    percent_removed = ((totalRemoval_g*2)/watershed_load)*100,
    storm = "Q0.5",
    river = "3_1", 
    data_freq = "10min")
```

###15-min data output frequency
```{r}
R31_15min_Q0.5 <- read_csv("FrequencyData/3_1_15min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_3rdO ~ 15)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>%
  mutate(
    removal_g = case_when(STA %in% c(143000, 101000) ~ (ti_tot_min/60)*(Xcs/2)*(w_3rdO*2)*k/1000,
                                    TRUE ~ (ti_tot_min/60)*Xcs*(w_3rdO*2)*k/1000))

Removal31_15min_Q0.5 <- R31_15min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g))%>%
  mutate(
    percent_removed = ((totalRemoval_g*2)/watershed_load)*100,
    storm = "Q0.5",
    river = "3_1", 
    data_freq = "15min")
```

#FOURTH ORDER
###10-min data output frequency
```{r}
R41_10min_Q0.5 <- read_csv("FrequencyData/4_1_10min_0.5Q_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_4thO ~ 10)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>%
  mutate(
    removal_g = case_when(STA %in% c(101000, 0) ~ (ti_tot_min/60)*(Xcs/2)*(w_4thO*2)*k/1000,
                           TRUE ~ (ti_tot_min/60)*Xcs*(w_4thO*2)*k/1000))

#for some reason  50 is not in the STA column. Instead there is an NA in place.

#cleanup. Don't know why the stations wont go in order automatically, probably bc they're a characters instead of numbers
R41_10min_Q0.5$STA <-  as.numeric(R41_10min_Q0.5$STA)
R41_10min_Q0.5 <- R41_10min_Q0.5[order(R41_10min_Q0.5$STA, decreasing = TRUE),]

Removal41_10min_Q0.5 <- R41_10min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g))%>%
  mutate(
    percent_removed = (totalRemoval_g/watershed_load)*100,
    storm = "Q0.5",
    river = "4_1", 
    data_freq = "10min")
```

###15-min data output frequency
```{r}
R41_15min_Q0.5 <- read_csv("FrequencyData/4_1_15min_0.5Q_full4th100p.csv") %>%
    mutate(sta = 
           case_when(
             endsWith(STA, ".*") ~ substr(STA, 1, nchar(STA)-2), #Clean up bc didn't edit out the .* in excel before uploading
             endsWith(STA, ".0*") ~ substr(STA, 1, nchar(STA)-3),
             endsWith(STA, ".00*") ~ substr(STA, 1, nchar(STA)-4),
             TRUE ~ STA)) %>%
  group_by(sta) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_4thO ~ 15)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>%
  mutate(
    removal_g = case_when(sta %in% c(101000, 0) ~ (ti_tot_min/60)*(Xcs/2)*(w_4thO*2)*k/1000,
                           TRUE ~ (ti_tot_min/60)*Xcs*(w_4thO*2)*k/1000))

#cleanup. Don't know why the stations wont go in order automatically, probably bc they're a characters instead of numbers
R41_15min_Q0.5$sta <-  as.numeric(R41_15min_Q0.5$sta)
R41_15min_Q0.5 <- R41_15min_Q0.5[order(R41_15min_Q0.5$sta, decreasing = TRUE),]

Removal41_15min_Q0.5 <- R41_15min_Q0.5 %>%
  summarise(
    totalRemoval_g = sum(removal_g))%>%
  mutate(
    percent_removed = (totalRemoval_g/watershed_load)*100,
    storm = "Q0.5",
    river = "4_1", 
    data_freq = "15min")

#write.csv(river41_15min, file = "Exports/river41_15min.csv")

Q0.5_freq_removal <- rbind(Removal17_5min_Q0.5, Removal17_10min_Q0.5, Removal17_15min_Q0.5,
                        Removal22_5min_Q0.5, Removal22_10min_Q0.5, Removal22_15min_Q0.5,
                        Removal31_5min_Q0.5, Removal31_10min_Q0.5, Removal31_15min_Q0.5,
                        Removal41_15min_Q0.5) %>%                   
  mutate_if(is.numeric, # Using dplyr functions
            round,
            digits = 4)
```

#Qmonth
##FIRST & SECOND ORDER:
###5-min data output frequency only
```{r}
R17_5min_Qm <- read_csv("FrequencyData/1_7_5min_Qm_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_1stO ~ 5)) %>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(165500, 159500) ~ (ti_tot_min/60)*(Xcs/2)*(w_1stO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_1stO*2)*k/1000))

Removal17_5min_Qm <- R17_5min_Qm %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*24)/watershed_load)*100,
     storm = "Qm",
    river = "1_7", 
    data_freq = "5min") 


R22_5min_Qm <- read_csv("FrequencyData/2_2_5min_Qm_full4th100p.csv") %>%
  group_by(STA) %>%
  mutate(
    ti_min = case_when(RtopW_ft >= w_2ndO ~ 5))%>%
  summarise(
    ti_tot_min = sum(ti_min, na.rm = TRUE)) %>% #how long each XS is inundated
  mutate(
    removal_g = case_when(STA %in% c(159500, 154000, 148500, 143000) ~ (ti_tot_min/60)*(Xcs/2)*(w_2ndO*2)*k/1000,
                                   TRUE ~ (ti_tot_min/60)*Xcs*(w_2ndO*2)*k/1000)) #all other XS have normal spacing  

Removal22_5min_Qm <- R22_5min_Qm %>%
  summarise(
    totalRemoval_g = sum(removal_g)) %>%
  mutate(
    percent_removed = ((totalRemoval_g*6)/watershed_load)*100,
    storm = "Qm",
    river = "2_2", 
    data_freq = "5min")

Qm_freq_removal <- rbind(Removal17_5min_Qm, Removal22_5min_Qm)
freq_removal <- rbind(Q1_freq_removal, Q0.5_freq_removal, Qm_freq_removal)
```
